Title

### 2013-02-15 inc/extension/initial_conditions/initial_conditions.tex
comment on bin model

>>>>

To test the validity of the simplistic model presented above I also designed a bin model that depends on nothing other than basic physics and a ``transmission'' function.
This function is the likelihood of emission by emission energy, the maximum energy being the the excess photoemission energy.

In the model the space in front of the photocathode is binned into segments in ranges of distance from the photocathode.
The laser pulse duration is then binned into slices of time for a total duration of $N \tau$ where the peak of the pulse occurs at $N \tau / 2$.
For each slice of time, one can determine the relative number of electrons generated in that slice (normalized to the total number that will be created by the end of the simulation), and the velocity distribution of those electrons.
Knowing the remaining time in the simulation and the acceleration due to the electric field, the velocity distribution can be used to place these electrons into final spatial bins.
Additionally, as the electrons are placed into these bins, their average velocity is stored as well.

This process repeats for each time slice until the finish time, at which point the laser has essentially stopped creating electrons.
At this time, the earliest fastest electrons will be a distance 
\begin{equation}
  d_{max} = v_0 N \tau + \frac{e E_{ DC }}{2 m} (N \tau)^2 
\end{equation}
away from the the photocathode, and the the electrons created in the last slice will be at $d=0$.
By counting the electrons in each spatial bin and fitting to a gaussian, we can determine $\sigma_z(0)$, the inital spatial uncertainty in the pulse.
Taking a weighted average of the velocity of the electrons in each spatial bin and fitting to a linear function across the pulse, we can determine the velocity (momentum) chirp $\gamma_z(0)$.
The shapes of the actual output compare well with the fitted functional form for both of these parameters for all reasonable ranges of field and laser pulse duration.

Finally the velocity uncertainty in each pulse can be computed, however unlike the previous parameters, the AG model only allows for a constant value of local momentum uncertainty across the pulse $\eta_z(0)$.
As seen in \ref{fig:bin_model} this limitation on functional form severely limits the accuracy with which the determined value of $\eta_z(0)$ represents the actual distribution of momentum uncertainties computed by the binning model.
